### 2016-08-20 ms/ms.tex
worked on disucssion

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
In contrast to the ordered network build-up described by preferential
attachment, assembly can be punctuated by significant reorganizations
of interactions \citep{peel2014detecting}. For example, as new species
are added, resident species change their interaction partners to
minimize competition, or become extinct. Such significant
reorganizations of interactions, or changing points, have been
observed in networks responding to abrupt shifts in the behavior of
interacters \citep{peel2014detecting}. No studies, however, have
examined whether changing points occur during ecological network
assembly.

@@

%% restoration of ecosystem services is really important, particularly
%% in ag. but ag is a bad place for pollinators
Facilitating effective restoration of networks is particularly
imperative in areas where species interactions provide essential
ecosystem services, such as crop pollination. In intensively managed
agricultural landscapes, the demand for pollination services is the
greatest \citep{kremen-2008-10}. However, honey bees, managed
extensively around the world to provide crop pollination, are in
global decline \citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In
addition, native pollinators, which have the capacity to provide
sufficient crop pollination \citep{kremen-2002-16816,
  winfree-2007-1105, kremen-2004-1109}, are in short supply because
these landscapes make poor habitats for pollinator populations
\citep{kremen-2002-16816}. To ensure provision the continued provision
of ecosystem services and curb biodiversity loss, effective
restoration of pollinators and their interactions in agricultural
landscapes is critical.

@@

% Pollinators are one such key group of interactors: $75\%$ of all
% crop species depend to some extent on pollinator visitation
% \citep{klein-2007-303}, and animal-pollinated crops supply a large
% proportion of essential nutrients to the human diet
% \citep{eilers-2011-e21363}.

@@

Flower-visitors to plants in hedgerows and unrestored controls were
netted for one hour of active search time (the timer was paused when
handling specimens). Honeybees (\textit{Apis mellifera}) were not
collected because their abundance is determined largely by the
placement of hives throughout the region by bee-keepers. All other
insect flower visitors that touched the reproductive parts of the
flower were collected; however, here we focus only on wild bees and
syrphids (representing 49 and 19 percent of records, respectively),
the most abundant and effective pollinators in the system (C. Kremen,
A.~ Klein and L.~ Morandin, unpublished data). Bee and syrphid specimens
were identified to species (or morpho-species for some bee specimens
in the genera \textit{Nomada} and \textit{Sphecodes}) by expert
taxonomists.

@@

We calculate species persistence as the proportion of the surveys a
pollinator was observed. Species observed consistently within and
between years are thus maximally persistent. Weighted species degree
is calculated from interaction observations observed in more extensive
data-set from Yolo County (approx.~ 18000 interaction records) that
included both the data included in this study and additional data from
sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. %% does this make sense to
%% calculate from an independent data set?
To represent the the variability of species within networks, we
computed the coefficient of variation of weighted closeness at each
site through time. Closeness describes the centrality of a species in
the network by calculating path lengths to other vertices (species) in
the graph. We used linear mixed models to test whether the variability
of species closeness values was related to the persistence or degree
of that species \citep{lme4, lmetest}. We included random effects for
species, as well as site. We focused on the pollinator species because
the hedgerow flowers are planted and thus are not directly
assembling. Because degree and persistence were strongly correlated,
($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), each explanatory variable
was included in the model separately. Because a linear increase in
closeness, as might be expected with assembly by preferential
attachment, would lead to a high variability in closeness scores, we
also test whether closeness increases through time.

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
The changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid (i.e., via preferential
attachment), nestedness would increase through time. Lastly, if the
network is accumulating specialist species or species are beginning to
limit their interaction niche breath as the network assembles, this
would lead to an increase in the network-level specialization
\citep{bluthgen-2006-9}. To test whether network modularity,
nestedness or specialization changed linearly with assembly, we used
linear mixed models with the descriptive network metrics as the
response variable, year of assembly as the explanatory variable, and
random effects of site and year.

We use NODF (weighted or unweighted) to evaluate network nestedness
\citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared between communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and the distribution of the interaction
frequencies \citep{Galeano2009}. Lastly, Network specialization was
measured using H2, which estimate the deviation of the observed
interaction frequency between plants and pollinators from a null
expectation where all partners interact in proportion to their
abundances \citep{bluthgen-2006-9}. It ranges from 0 for generalized
networks to 1 for specialized networks.
\subsection*{Network structure}

The changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular community
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid, nestedness would increase
through time. Alternatively, if the network is accumulating specialist
species or if species are beginning to limit their interaction niche
breath as the network assembles, this would lead to an increase in the
network-level specialization \citep{bluthgen-2006-9} and nestedness
would decrease through time. To test whether network modularity,
nestedness or specialization changed linearly with assembly, we used
linear mixed models with the descriptive network metrics as the
response variable, year of assembly as the explanatory variable, and
random effects of site and year.

@@

The majority ($76\%$) of the sites tests underwent at least one
significant reorganization of interactions (Fig.~
\ref{fig:changePoints}).  All five of the assembling hedgerows
experienced changing points, whereas only $40\%$ and $81\%$ of
non-assembling hedgerows and field margins, respectively, underwent
significant interaction reorganizations. Assembling hedgerows
experienced significantly more changing points than the non-assembling
networks (difference in the odds ratios between assembling and
non-assembling networks, $3.316$, $95\%$ CI $[1.314, 8.572]$,
$p$-value= $0.0117$). Network assembly following restoration is thus
punctuated by more interaction reorganizations than would be expected
by environmental shifts that would effect assembling and
non-assembling networks equally.

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/changePoint/plotting/networks.pdf}
  \caption{The network structure and changing points (vertical red
    lines) in assembling hedgerows and a representative sample of
    non-assembling hedgerows and weedy field margins. In each network,
    plants and pollinators are represented by green and yellow
    circles, respectively, weighted by their degree. Each species has
    has a consistent position in the network across years. In the
    assembling hedgerows, colored circles in the corner of each
    network represent the years post restoration.}
  \label{fig:changePoints}
\end{figure}
\clearpage

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly (estimate of
the slope of nestedness through time $\pm$ standard error of the
estimate, $1.834 \pm 0.6142$, $p$-value=$0.022$, Fig.~
\ref{fig:baci}).  Modularity decreased (Fig.~ \ref{fig:baci}), though
the slope was not significantly different from zero (estimate of the
slope of modularity through time $\pm$ standard error of the estimate,
$-0.524$ $\pm$ $0.295$, $p$-value=$0.124$). Specialization remained
relatively constant (estimate of the slope of specialization through time
$\pm$ standard error of the estimate, $0.003$ $\pm$ $0.015$,
$p$-value=$0.827$).

@@

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species where removed incrementally by degree
(estimate of the slope of robustness through time $\pm$ standard error
of the estimate, $6*10^{-5} \pm 4*10^{-3}$, $p$-value=$0.987$) or
abundance ($0.001 \pm 0.003$, $p$-value=$0.65$, Fig.~ \ref{fig:rob}).

In contrast, the robustness of networks to perturbation, as measured
by the algebraic connectivity of the network, increased as the network
assembled (estimate of the slope of robustness through time $\pm$
standard error of the estimate, $0.6814 \pm 0.272$, $p$-value=$0.042$,
Fig.~ \ref{fig:rob}).

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where patterns of
interactions undergo several significant reorganizations. These
network organizations are unlikley to be a project of environmental
forces because the changing points in non-assembling communities are
both less frequent and in different time points. The reorganizations
are thus a product of the assembly process.

There were no consistent trends in when change points occurred within
assembling hedgerows or across all sites, except many sites had
changing points between year 2009 and 2011 (Fig.~
\ref{fig:changePoints}). In California, 2011 marked the beginning of a
multi-year drought. In the assembling hedgerows were not sampled in
2010, so disentangling whether the changing points are due to skipping
a year of assembly or the drought is not impossible. Interestingly,
most of the assembling hedgerows did not undergo a signficiant
reorganization of interactions immediatly the hedgerow was planted
(i.e., the transition from weedy field margin to hedgerow). This
result is consistent with other studies finding that the gains in
species richness of both the plant and pollinators takes several years
post-restoration (Kremen and M'Gonigle, in prep).

Surprisingly, the species that were most variable in their network
position and thus contributed most to network reorganizations where
species with the highest degrees (i.e., most generalized) and
persistence.  For example, the five most ubiquitous species in our
study landscape --- \textit{Halictus ligatus}, \textit{Halictus
  tripartitus},\textit{Lasioglossum (Dialictus) incompletum}, and
\textit{Toxomerus marginatus} --- where also the only species that
changed what module (i.e., community) they were present in across
years in all of the assembling hedgerows. Because species degree and
persistence were strongly correlated, it is difficult to disentable
the causal mechanism for why species with their chatacterists are so
variable in their network position. Generalized species may be best
able to exploit the limited floral resources the intensivly managed
agriculture landscape, and thus also most persistent. These adaptable
species will take advanatge of the most advantage resources, which my
depend the other pollinator species that are present and the state of
the floral resource. More persistent species also have longer
phenologies, so they have the opportunity to visit many different
flowers, resulting in a high degree. Either way, our results suggest
that given the opportunity and ability to use different resources,
species will often their network positions.

@@

The frequent changing points in network organization, dynamic nature
of the location of species in networks, and turnover of species and
nodes all point to an assembly mechanism other than preferential
attachment. Nestedness did increase with years post restoration, as
would be expected if colonizing, specialist species attached to a
central, generalist core. With preferential attachment, however, we
could also expect connectance and specialization to increase, and see
neither. The increase in nestedness is thus more likely a consequence
of the enhancement of species richness through time \flagged{DO WE
  HAVE CITATIONS FOR THIS?}. In addition, though the colonization and
persistence of floral specialists increases with assembly
\citep{mgonigle-2015-x}, this must be accumpanied changes in the diet
breat of the present species in order for network-level specialization
to remain constant through time.

Preferential attachment is the most widely accepted theory explaining
network assembly, but few ecological studies have been conducted that
test for this mechanism \citep{Olesen2008}. \flagged{other
  citations??}. Though \cite{Olesen2008} found some evidence for an
assmbly process like prefrential attachment governming the temporal
build up of plant-pollinator networks within a season, the frequent
reorganizations of the hedgerow communities suggest a very different
mechanism is at play. Plant-pollinator networks in general are highly
dynamic, with high turnover of species and interactions both within
and between seasons \citep{Burkle2011}. Though our non-assembling
communities experience fewer network reorganizations than the
assembling hedgerows, $82\%$ of field marings and $40\%$ of mature
hedgerows underwent at least one changing point in network
structure. Few alternative models to perferential attachment that
predict these network reorganizations have been explored, however.

Complementarity between traits like tounge length and corolla depth as
well as body and flower impose some biophysical limits to the
interactions between plants and pollintors
\citep{Vazquez2009evaluating, Stang2009, Stang2006,
  Santamaria2007}. Similarly, the phenologies of plants and
pollinators must also overlap \citep{Vazquez2009,
  Vazquez2009evaluating}.

 \citep{valdovinos2013adaptive}

The changes in network patterns with assembly also increased the
robustness of the networks to perturbation, but not to plant species
loss.

The increase in nestedness has been related to an increase in the
robustness of communities to species extinctions because the core of
generalist species would act as a buffer against species loss
(REF). Similarly, communities with greater modularity would be more
robust in general, because modules would act as a buffer against
perturbation spreading and the pervasive effects of species loss. We
expected that as communities assemble and species richness increase,
communities would become increasingly robust to species loss. however,
we found that robustness to species loss did not change through
time. This is interestingly from the conservation biology point of
view, because even early assembling communities seem to be as robust
as more mature communities, despite the richness insurance
hypothesis. However, communities are not only subjected to species
loss, but also to other types of perturbations that can cascade
through the network. Gaiarsa et al. (submitted) suggest using
algebraic connectivity to explore how vulnerable ecoogical communities
might be to cascading effects. Our results indicate that more mature
communities are more robust to cascading effects than early on
assemblages, and that this result is related to species richness. This
migth be related to XX....

@@

We would like to thank Paulo Guimar{\~a}es Leto Peel and Aaron Clauset for
their invaluable discussions and for help with the change point
analysis.  We thank the growers and land owners that allowed us to
work on their property.  We also greatly appreciate the identification
assistance of expert taxonomists Martin Hauser, Robbin Thorp and Jason
Gibbs.  This work was supported by funding from the Army Research
Office (W911NF-11-1-0361 to CK), the Natural Resources Conservation
Service (CIG-69-3A75-12-253, CIG-69-3A75-9-142, CIG-68-9104-6-101 and
WLF-69-7482-6-277 to The Xerces Society), the National Science
Foundation (DEB-0919128 to CK), The U.S.  Department of Agriculture
(USDA-NIFA 2012-51181-20105 to Michigan State University).  Funding
for LCP was provided by an NSF Graduate Research Fellowship and the
USDA NIFA Graduate Fellowship. Funding for MPG was provided by S{\~a}o
Paulo Research Foundation (FAPESP, grant 2013/13319-5).

@@

>>>>

%% there are other ways to assemble that are not preferentia;
%% attchment, particularly vis big reorganizations of interactions
In contrast to the ordered network build-up described by preferential
attachment, assembly can be punctuated by significant reorganizations
of interactions \citep{peel2014detecting}. Such significant
reorganizations of interactions, or changing points, have been
observed in social networks responding to abrupt shifts in the
behavior of interactors \citep{peel2014detecting}.  In ecological
communities, such shifts my occur if, as new species are added,
resident species change their interaction partners to optimize their
foraging effort. In plant-pollinator communities, theory predicts
pollinators optimize their use of floral resources to reduce
interspecific competition and improve resource-use efficiency
\citep{pyke1984optimal, valdovinos2010consequences,
  valdovinos2013adaptive, albrecht2010plant, Bluthgen2007}. No
studies, however, have examined whether changing points occur during
ecological network assembly and how they relate to the behavior of the
interactors.

@@

%% restoration of ecosystem services is really important, particularly
%% in ag. but ag is a bad place for pollinators
Facilitating effective restoration of networks is especially
imperative in areas where species interactions provide essential
ecosystem services, such as crop pollination. In intensively managed
agricultural landscapes, the demand for pollination services is the
greatest \citep{kremen-2008-10}. However, honey bees, managed
extensively around the world to provide crop pollination, are in
global decline \citep{neumann-2010-1, van-engelsdorp-2009-e6481}. In
addition, native pollinators, which have the capacity to provide
sufficient crop pollination \citep{kremen-2002-16816,
  winfree-2007-1105, kremen-2004-1109}, are in short supply because
these landscapes make poor habitats for pollinator populations
\citep{kremen-2002-16816}. To ensure provision the continued provision
of ecosystem services and curb biodiversity loss, effective
restoration of pollinators and their interactions in agricultural
landscapes is critical.

@@

@@

Flower-visitors to plants in hedgerows and unrestored controls were
netted for one hour of active search time (the timer was paused when
handling specimens). Honeybees (\textit{Apis mellifera}) were not
collected because their abundance is determined largely by the
placement of hives throughout the region by bee-keepers. All other
insect flower visitors that touched the reproductive parts of the
flower were collected; however, here we focus only on wild bees and
syrphids (representing 49 and 19 percent of records, respectively),
the most abundant and effective pollinators in the system (C. Kremen,
A.~Klein and L.~Morandin, unpublished data). Bee and syrphid specimens
were identified to species (or morpho-species for some bee specimens
in the genera \textit{Nomada} and \textit{Sphecodes}) by expert
taxonomists.

@@

We calculate species persistence as the proportion of the surveys a
pollinator was observed. Species observed consistently within and
between years are thus maximally persistent. Weighted species degree
is calculated from interaction observations observed in more extensive
data-set from Yolo County (approx.~18000 interaction records) that
included both the data included in this study and additional data from
sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. %% does this make sense to
%% calculate from an independent data set?
To represent the the variability of species within networks, we
computed the coefficient of variation of weighted closeness at each
site through time. Closeness describes the centrality of a species in
the network by calculating path lengths to other vertices (species) in
the graph. We used linear mixed models to test whether the variability
of species closeness values was related to the persistence or degree
of that species \citep{lme4, lmetest}. We included random effects for
species, as well as site. We focused on the pollinator species because
the hedgerow flowers are planted and thus are not directly
assembling. Because degree and persistence were strongly correlated,
($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), each explanatory variable
was included in the model separately. Because a linear increase in
closeness, as might be expected with assembly by preferential
attachment, would lead to a high variability in closeness scores, we
also test whether closeness increases through time.

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Any changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main structural patterns
--- modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. In modular networks,
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid (i.e., via preferential
attachment), nestedness would increase through time. Lastly, if the
network is accumulating specialist species or species are beginning to
limit their interaction niche breath as the network assembles, this
would lead to an increase in the network-level specialization
\citep{bluthgen-2006-9}. To test whether network modularity,
nestedness or specialization changed linearly with assembly, we used
linear mixed models with the descriptive network metrics as the
response variable, year of assembly as the explanatory variable, and
random effects of site and year.

We use NODF (weighted or unweighted) to evaluate network nestedness
\citep{nodf}. NODF evaluates whether species with fewer partners
interact with subsets of partners with which more connected species
interact \citep{nodf}. To estimate modularity, we use a hierarchical
clustering algorithm \citep{Newman2004, igraph}.  We calculated
standardized $z$-scores so that nestedness and modularity metrics
could be compared between communities. The $z$-scores were calculated
by generating an ensemble of $999$ randomly assembled communities,
subtracting the mean of the statistic calculated across these
communities from the observed value, and then dividing by the standard
deviation. To assemble random communities, we reshuffled the
interactions between species but fixed the total number of
interactions, species and the distribution of the interaction
frequencies \citep{Galeano2009}. Lastly, Network specialization was
measured using H2, which estimate the deviation of the observed
interaction frequency between plants and pollinators from a null
expectation where all partners interact in proportion to their
abundances \citep{bluthgen-2006-9}. It ranges from 0 for generalized
networks to 1 for specialized networks.

@@

The majority ($76\%$) of the sites tests underwent at least one
significant reorganization of interactions
(Fig.~\ref{fig:changePoints}).  All five of the assembling hedgerows
experienced changing points, whereas only $40\%$ and $81\%$ of
non-assembling hedgerows and field margins, respectively, underwent
significant interaction reorganizations. Assembling hedgerows
experienced significantly more changing points than the non-assembling
networks (difference in the odds ratios between assembling and
non-assembling networks, $3.316$, $95\%$ CI $[1.314, 8.572]$,
$p$-value= $0.0117$). Network assembly following restoration is thus
punctuated by more interaction reorganizations than would be expected
by environmental shifts that would effect assembling and
non-assembling networks equally.

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/changePoint/plotting/networks.pdf}
  \caption{The network structure and changing points (vertical red
    lines) in assembling hedgerows and a representative sample of
    non-assembling hedgerows and weedy field margins. In each network,
    plants and pollinators are represented by green and yellow
    circles, respectively, weighted by their degree. Each species has
    has a consistent position in the network across years. In the
    assembling hedgerows, colored squares in the corner of each
    network represent the years post restoration.}
  \label{fig:changePoints}
\end{figure}
\clearpage

@@

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly (estimate of
the slope of nestedness through time $\pm$ standard error of the
estimate, $1.834 \pm 0.6142$, $p$-value=$0.022$, Fig.~
\ref{fig:baci}).  Modularity decreased (Fig.~\ref{fig:baci}), though
the slope was not significantly different from zero (estimate of the
slope of modularity through time $\pm$ standard error of the estimate,
$-0.524$ $\pm$ $0.295$, $p$-value=$0.124$). Specialization remained
relatively constant (estimate of the slope of specialization through time
$\pm$ standard error of the estimate, $0.003$ $\pm$ $0.015$,
$p$-value=$0.827$).

@@

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species where removed incrementally by degree
(estimate of the slope of robustness through time $\pm$ standard error
of the estimate, $6*10^{-5} \pm 4*10^{-3}$, $p$-value=$0.987$) or
abundance ($0.001 \pm 0.003$, $p$-value=$0.65$, Fig.~\ref{fig:rob}).

In contrast, the robustness of networks to perturbation, as measured
by the algebraic connectivity of the network, increased as the network
assembled (estimate of the slope of robustness through time $\pm$
standard error of the estimate, $0.6814 \pm 0.272$, $p$-value=$0.042$,
Fig.~\ref{fig:rob}).

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations. These network organizations
are unlikely to be a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and there are few consistent trends in when change points
occurred across all sites. Several sites had changing points between
year 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. In the assembling
hedgerows were not sampled in 2010, so disentangling whether the
changing points are due to skipping a year of assembly or the drought
is not impossible. Interestingly, most of the assembling hedgerows did
not undergo a significant reorganization of interactions immediately
the hedgerow was planted (i.e., the transition from weedy field margin
to hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have a
significant impact on the plant-pollintor communities (Kremen and
M'Gonigle, in prep).

TRANSITION... Surprisingly, the species that were most variable in
their network position and thus contributed most to network
reorganizations where species with the highest degrees (i.e., most
generalized) and persistence.  For example, the five most ubiquitous
species in our study landscape --- \textit{Halictus ligatus},
\textit{Halictus tripartitus},\textit{Lasioglossum (Dialictus)
  incompletum}, and \textit{Toxomerus marginatus} --- were also the
only species that changed what module (i.e., community) they were
present in across years in all of the assembling hedgerows. Because
species degree and persistence were strongly correlated, it is
difficult to disentangle the causal mechanism for why species with
those characteristics are so variable in their network
position. Generalized species may be best able to exploit the limited
floral resources the intensively managed agriculture landscape, and
thus also most persistent. More persistent species also have longer
phenologies, so they have the opportunity to visit many different
flowers, resulting in a higher degree. Either way, our result suggests
that adaptable species can change their network position to utilize
the most advantageous floral resources, which my depend the other
pollinator species that are present and the state of the floral
resource. Thus given the opportunity and ability to use different
resources, species will often change their network positions.

@@

The frequent changing points in network organization, dynamic nature
of the location of species in networks, and turnover of species and
nodes all point to an assembly mechanism other than preferential
attachment. Nestedness did increase with years post restoration, as
would be expected if colonizing, specialist species attached to a
central, generalist core \cite{albrecht2010plant}. With preferential
attachment, however, we would also expect connectance and
specialization to increase, and see no such trends. The stable level
of network-level specialization through the assembly process may be
due to the increased colonization of specialized species
\citep{mgonigle-2015-x} accompanied by an increase in the diet breath
of resident species. This would be expected if resident species were
able to minimize their foraging time by expanding their diet breath as
plant diversity increases with hedgerow maturation \citep{Waser1996,
  pyke1984optimal, Bluthgen2007, albrecht2010plant}. Such a change in
pollinator behavior would also explain the increase in network
nestedness.

The changes in network patterns with assembly also increased the
robustness of the networks to perturbation -- providing further
evidence that hedgerows are valuable tool for promoting species
conservation and ecosystem provision in agricultural areas
\citep{mgonigle-2015-x, ponisio2015farm, kremen-2015-602}. Because the
time it takes for a perturbation to spread through a network, as
measured by algebraic connectivity, is correlated with species
richness, the increase and plant and pollinator richness following
restoration is at least partially responsible for enhancing network
robustness. SOMETHING ABOUT DIVERSITY AND STABILITY

Interestingly, however, the robustness of hedgerow communities to
species loss did not change with assembly. This is particularly
surprising given the observed increase in nestedness, which is often
associated with an enhanced in robustness to extinction
\citep{Memmott2004}. It may be that assembling hedgerows have not yet
reached a sufficient level of nestedness to realize its
benefits. Nestedness of the assembling hedgerows, however, did not
asymptote within the eight years following restoration that the sites
were surveyed, so hedgerow networks may eventually reach sufficient
levels of nestedness to gain the robustness advantage.

Plant-pollinator networks in general are highly dynamic, with high
turnover of species and interactions both within and between seasons
\citep{Burkle2011}. Though our non-assembling communities experience
fewer network reorganizations than the assembling hedgerows, $82\%$ of
field margins and $40\%$ of mature hedgerows underwent at least one
changing point in network structure. Pollinators are also highly
opportunistic \citep{petanidou-2008-564, Vazquez2005b,
  albrecht2010plant}, though trait complementarity such as tongue
length and corolla depth impose some biophysical limits to the
interactions between plants and pollinators
\citep{Vazquez2009evaluating, Vazquez2009, Stang2009, Stang2006,
  Santamaria2007}. Such opportunism may buffer plant-pollinator
communities from global change \citep[e.g.,][]{ramos2012topological,
  kaiser2010robustness}, but our limited understanding of the assembly
of these communities impedes making such predictions
\citep{Vazquez2009, Burkle2011}. Unlike in the broader food web
literature, we have few mechanistic models of mutualistic network
assembly \citep{valdovinos2013adaptive}. In addition, the few that
have been developed often borrow their mechanisms from competitive
interactions, leading to inaccurate biological assumptions
\citep{holland2006comment}. We need further development of mechanistic
models of mutualistic stystem to generate testable predictions, along
with empirical exploration of network assembly. Plant-pollinator
communities and mutualisms in general are vital for the maintenance of
biodiversity and the provision of essential ecosystem services. We
must therefore understand the processes underlying their assembly to
facilitate restoration and conservation.

% Though \cite{Olesen2008} found some evidence for an
% assmbly process like prefrential attachment governing the temporal
% build up of plant-pollinator networks within a season, the frequent
% reorganizations of the hedgerow communities suggest a very different
% mechanism is at play.

@@

We would like to thank Paulo Guimar{\~a}es and Aaron Clauset for their
invaluable discussions, and Leto Peel for help with the change point
analysis.  We thank the growers and land owners that allowed us to
work on their property.  We also greatly appreciate the identification
assistance of expert taxonomists Martin Hauser, Robbin Thorp and Jason
Gibbs.  This work was supported by funding from the Army Research
Office (W911NF-11-1-0361 to CK), the Natural Resources Conservation
Service (CIG-69-3A75-12-253, CIG-69-3A75-9-142, CIG-68-9104-6-101 and
WLF-69-7482-6-277 to The Xerces Society), the National Science
Foundation (DEB-0919128 to CK), The U.S.  Department of Agriculture
(USDA-NIFA 2012-51181-20105 to Michigan State University).  Funding
for LCP was provided by an NSF Graduate Research Fellowship and the
USDA NIFA Graduate Fellowship. Funding for MPG was provided by S{\~a}o
Paulo Research Foundation (FAPESP, grant 2013/13319-5).

@@

% The increase in nestedness has been related to an increase in the
% robustness of communities to species extinctions because the core of
% generalist species would act as a buffer against species loss
% (REF). Similarly, communities with greater modularity would be more
% robust in general, because modules would act as a buffer against
% perturbation spreading and the pervasive effects of species loss. We
% expected that as communities assemble and species richness increase,
% communities would become increasingly robust to species loss. however,
% we found that robustness to species loss did not change through
% time. This is interestingly from the conservation biology point of
% view, because even early assembling communities seem to be as robust
% as more mature communities, despite the richness insurance
% hypothesis. However, communities are not only subjected to species
% loss, but also to other types of perturbations that can cascade
% through the network. Gaiarsa et al. (submitted) suggest using
% algebraic connectivity to explore how vulnerable ecoogical communities
% might be to cascading effects. Our results indicate that more mature
% communities are more robust to cascading effects than early on
% assemblages, and that this result is related to species richness. This
% migth be related to XX....
